---
title: "Analysis of Chicken Weights in R"
author: "Sarah AlQahtani"
date: "10/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
library(tidyverse)
library(DT)
```
### Description of chickwts dataset
An experiment was conducted to measure and compare the effectiveness of various feed supplements on the growth rate of chickens.

# Analysis of Chicken Weights {.tabset .tabset-fade .tabset-pills}
## Part 1: Exploratory Data Analysis
```{r}
knitr::kable(summary(chickwts))
```

```{r}
glimpse(chickwts)
```
A data frame with 71 observations on the following 2 variables.

weight: a numeric variable giving the chick weight.

feed: a categorical variable giving the feed type.

## Part 2: Descriptive Statistics
```{r}
datatable(chickwts %>%
  group_by(feed) %>%
    summarise(No_Obs=length(feed),
              Avrage_Weight=mean(weight),
              Std_Weight=sd(weight)))
```

## Part 3: Plots
```{r}
ggplot(chickwts,aes(feed,weight))+
  geom_boxplot()
```

```{r}
ggplot (chickwts, aes(feed, weight)) +
  geom_jitter(width = 0.3) +
  stat_summary(fun.data = mean_sdl, 
               fun.args = list(mult = 1), 
               col = "red")
  
```

## Part 4: Inferential Statistics
### The one-way ANOVA summary:
```{r}
knitr::kable(anova(lm(weight ~ feed, data = chickwts)))
```
ANOVA test gives us a p-value way below the .05 threshold.


### Tukey’s Post-hoc test:
```{r}
datatable(TukeyHSD(aov(weight~feed,data =chickwts))$feed)
```
In Tukey’s Post-hoc test, we find significant differences in these pairs of variables:

* horsebean-casein
* linseed-casein
* soybean-casein
* meatmeal-horsebean
* sunflower-horsebean
* sunflower-linseed
* andsunflower-soybean
* linseed-casein

### End tabset

